Tampering Detection In Low-Power \\ Smart Cameras

### 2015-06-22 paper.tex
Section IV, including caption

The most computationally demanding operations of Algorithm \ref{alg:DISPL} consist in computing of the indicators, in particular $g$. Computing $g$ requires, when using the Sobel filters in~\eqref{eq:normaGradiente}, $34$ operations per pixels\footnote{Execution can be accelerated whether hardware implementations of the FFT transform are available}, while computing $l$ and $d$ requires 1 and 3 operations per pixel, respectively. Detecting outliers in the indicators requires two comparisons per frame: thus, monitoring regions instead of the whole image has a negligible impact on the overall computational complexity. Algorithm~\ref{alg:DISPL} has very low memory requirements: $l$ and $g$ indicators can be computed online, while $d$ requires to store a single frame in memory. Segmentation is executed only during the initial configuration and can be performed on an external device connected to the smart camera. As such, Algorithm~\ref{alg:DISPL} can be properly executed on low-power and ultra low-power cameras.
%\gi{Adriano: inserisci qui l'algoritmo e traducilo in inglese. Se riusciamo lo spostiamo prima di tutte le sottosezioni}
\vspace{-0.2cm}
\section{Experiments}\label{sec:experiments}
Experiments are meant to assess the advantages of separately monitoring regions in a tampering-detection framework like Algorithm~\ref{alg:DISPL}. To this purpose, we show that Algorithm~\ref{alg:DISPL} outperforms a solution monitoring the indicators on the whole image (\emph{Total} in Figure~\ref{fig:ROC}). We also show that image regions have to be adaptively defined on the image content, and that operating on a Voronoi partition of the scene in $K$ regions obtained by clustering $[r(x), c(x)]$ leads to performance loss (\emph{Voronoi} in Figure~\ref{fig:ROC}). For both regions defined as in Section~\ref{subsec:Segmentation} and Voronoi regions, we test the two extreme cases where $\Gamma_l = 1$ and $\Gamma_l = K-1$ (respectively, $\Gamma_d = 1$ and $\Gamma_d = K-1$).

We recorded $8$ sequences from webcams monitoring different urban areas, yielding overall $24410$ frames. From each frame we have cropped the central area, removing the 50 top-most and bottom-most rows, and the 50 left-most and right-most columns. We have synthetically introduced $10\%$ of tampered frames: displacements have been simulated by moving the central cropping area of a random shift having magnitude between 20 and 50 rows and coulumns (as in Figure \ref{fig:sequences}(b)). Blurring  (as in Figure \ref{fig:sequences}(a)) was simulated by convolution against a Gaussian kernel, with $1\leq\sigma\leq5$ randomly taken. \footnote{Sequences can be released upon request.}.
%\gi{Adriano: image sizes? blur kernel std? quanti pixel il displacement?}
%The second dataset was recorded using a Raspberry Pi Model B+ \cite{raspberry} mounting a camera module. 
%Few sequences of the first dataset contain real tampering events  (Figure \ref{fig:indicatori}). 
%In the second dataset, tampering was introduced by moving the device or spraying water on the camera lens.

The typical figure of merit for assessing detection performance in one-shot monitoring methods are the Receiver-Operating Characteristic (ROC) curves: in our case, these can be computed by varying $\gamma_l$, $\gamma_d$ and $\gamma_g$ in a range of values between $0.1$ and $50$, with step $0.1$. In particular, each point in the ROC curve report a pair of values (1-SPECIFICITY$_\gamma$, RECALL$_\gamma$) defined as
\[1-\text{SPECIFICITY}_\gamma = \frac{\text{FP}_\gamma}{\text{TN}_\gamma+\text{FP}_\gamma}, \ \text{ and } \ \text{RECALL}_\gamma=\frac{\text{TP}_\gamma}{\text{TP}_\gamma+\text{FN}_\gamma}\]
where TP$_\gamma$ represents the number of true positives (tampered frames correctly detected), FP$_\gamma$ of false positives (tampering-free frames detected), TN$_\gamma$ of true negatives (tampering-free frames not detected) and FN$_\gamma$ of false negatives (missed tampered frames), for a given value of $\gamma$.
\vspace{-0.3cm}
\subsubsection{Discussion}
ROC curves in Figure~\ref{fig:ROC}(a)-(b) and the Area Under the Curve (AUC) values reported in the caption indicate that camera displacements can be effectively detected by all the considered methods; the comparison against Voronoi regions suggests that a more substantial advantage is guaranteed when regions fit the scene content. As far as the values of $\Gamma_l$ and $\Gamma_d $ are concerned, the best option is to raise an alert as soon as a single region provides a very clear outlier (i.e., interval \eqref{eq:confidenceRegions} are quite wide). This option is preferable with respect to requiring $K-1$ regions to simultaneously fire an outlier, because it also enable the detection of partial occlusions of the scene.\\
Considering $d$ as indicator, we observe that to limit FPs to $1\%$, Algorithm~\ref{alg:DISPL} have a recall of $99.92\%$, with $\gamma = 15.6$, while considering the whole image solution decreases TPs to $91.67\%$ ($\gamma = 6.5$), as for considering Voronoi's regions ($89.05\%$, $\gamma = 18.64$).
Considering $l$ as indicator, instead, limit FPs to $1\%$ brings a recall of $73.98\%$ when using Algorithm~\ref{alg:DISPL} ($\gamma=5.8$), more than considering the whole image solution ($17.85\%$, $\gamma=3.7$), and Voronoi's regions ($53.02\%$, $\gamma=6$).
Having few false alarms is important in a low-power context, considering the high number of frames that have to be processed. Most importantly, false alerts are halved basically at no computational overhead.
Finally, ROC curves confirm that $d$ is a far more effective indicator than $l$ in detecting camera displacements.\\ %\gi{Aggiornare con i nuovi dati}
%\emph{Considering $d$ as indicator, we observe that to achieve a recall of $98\%$, Algorithm~\ref{alg:DISPL} operates at $0.4\%$ of false alarms, with $\gamma = 24.7$, which is less than one fifth of the whole image solution ($2.2\%$ with $\gamma = 4.6$) and the Voronoi solution ($2.3\%$ with $\gamma = 12.9$).
%On the other side, considering $l$ as indicator, we observe that to achieve a recall of $98\%$, Algorithm~\ref{alg:DISPL} operates at $13\%$ of false alarms, with $\gamma = 2.5$, which is about one sixth of the whole image solution ($75\%$ with $\gamma = 0.1$) and about three fifty than the Voronoi solution ($22\%$ with $\gamma = 1.7 $).
%Having few false alarms is important in a low-power context, considering the high number of frames that have to be processed. Most importantly, false alerts are halved basically at no computational overhead.} \gi{Aggiornare con i nuovi dati}
In contrast, Figure~\ref{fig:ROC}(c) confirms that blurring is more effectively detected by monitoring the whole scene at once. This is probably due to the fact that typically, regions $\{R_k\}$ do not include the most prominent edge of the scene, which are indeed the most informative part to detect blurring. This is the reason why, in Algorithm~\ref{alg:DISPL}, $g$ is monitored on the whole image.%\gi{aggiungere commento su K-1 vornoi che va meglio?}

\begin{figure}[t]
\centering
\includegraphics[width=1\linewidth]{Immagini/curve}
\caption{\textbf{(a)} ROC curves relative to displacement detection based on FD: the AUC obtained by 
``One region - Algorithm 1'' is $99.89\%$, while the AUC obtained by ``Total'' (on the whole 
image) is $99.65\%$.
\textbf{(b)} ROC curves relative to displacement detection based on Luma: the AUC obtained by 
``One region - Algorithm 1'' is $98.44\%$, while the AUC obtained by ``Total'' (on the whole 
image) is $84.07\%$.
\textbf{(c)} ROC curves relative to blurring detection based on Gradient: as opposed to \textbf{(a)} and 
\textbf{(b)}, ``One region - Algorithm 1'' (AUC $98.4\%$) is outperformed by ``Total'' (AUC $99.13\%$).
Note that, in order to highlight the details, the ROC curves are drawn with different 
scales.}
%\caption{\textbf{(a)} ROC curve for displacement detection considering Frame Difference (FD) as indicator.
%	%There is an improvement in the performance considering adaptive regions w.r.t. considering the whole image or Voronoi regions.
%	The AUC corresponding to Algorithm~\ref{alg:DISPL} ($1$ region - Algorithm $1$) is $99.89\%$, while the AUC of considering the whole image (Total) is $99.65\%$. 
%	%the AUC of Luma-Voronoi is $99.85\%$, and the AUC of Frame-Difference is $99.44\%$ (axis have been zoomed for the visualization sake). Large AUC values indicate that these displacements can be successfully detected and that Algorithm~\ref{alg:DISPL} is the most effective one.
%	\textbf{(b)} ROC curve for displacement detection considering Luma as indicator.
%	%There is an improvement in the performance considering adaptive regions w.r.t. considering the whole image or Voronoi regions.
%	The AUC corresponding to Algorithm~\ref{alg:DISPL} ($1$ region - Algorithm $1$) is $98.44\%$, while the AUC of considering the whole image (Total) is $84.07\%$. 
%	\textbf{(c)} ROC curve for blurring detection.
%	In this case, the Gradient-Total (AUC $99.13\%$) outperforms the Gradient-Regions (AUC $98.4\%$) because this latter do not include the most prominent edges in images, which are the most important information to detect blurring. %This is the reason why, in Algorithm~\ref{alg:DISPL}, $g$ is monitored on the whole image. 
%	ROC curves \textbf{(a)} and \textbf{(c)}
%	%For the visualization sake, ROC curves \textbf{(a)} and \textbf{(c)} have been reported in a limited range of both axis, and in particular we focus on low values of 1-SPECIFICITY, thus of false alarms.
	%}
\label{fig:ROC}
\end{figure}
%\begin{figure}[htb]
%\centering
%\subfigure[]{\label{fig:buenosAiresDef}\includegraphics[width=0.45\linewidth]{Immagini/ROCdefocus1}}
%\subfigure[]{\label{fig:buenosAiresDispl} \includegraphics[width=0.45\linewidth]{Immagini/ROCdefocus_fd}}
%\caption{ROC curves for defocus detection, considering three alternative approaches. \textbf{(a)} Analysis of the mean gradient energy. \textbf{(b)} Analysis of the frame differencing.}
%\label{fig:ROCdisplacement}
%\label{fig:ROCdefocus}
%\end{figure}

>>>>

The most computationally demanding operations of Algorithm \ref{alg:DISPL} consist in computing of the indicators, in particular $g$. Computing $g$ requires, when using the Sobel filters in~\eqref{eq:normaGradiente}, $34$ operations per pixels\footnote{Execution can be accelerated whether hardware implementations of the FFT transform are available}, while computing $l$ and $d$ requires 1 and 3 operations per pixel, respectively. Detecting outliers in the indicators requires two comparisons per frame: thus, monitoring regions instead of the whole image has a negligible impact on the overall computational complexity. Algorithm~\ref{alg:DISPL} has very low memory requirements: $l$ and $g$ indicators can be computed online, while $d$ requires to store a single frame in memory. Segmentation is executed only during the initial configuration and can be performed on an external device connected to the smart camera. As such, Algorithm~\ref{alg:DISPL} can be properly executed on low-power and ultra low-power cameras.
%\gi{Adriano: inserisci qui l'algoritmo e traducilo in inglese. Se riusciamo lo spostiamo prima di tutte le sottosezioni}
\vspace{-0.2cm}
\section{Experiments}\label{sec:experiments}
Experiments are meant to assess the advantages of separately monitoring regions in the considered tampering-detection framework. To this purpose, we show that Algorithm~\ref{alg:DISPL} detects camera displacements better than monitoring indicators on the whole image (\emph{Whole Image} in Figure~\ref{fig:ROC}). We also show that it is important to define regions considering the scene content, since operating on $K$ regions obtained by clustering $[r(x), c(x)]$ leads to performance loss (\emph{Voronoi} in Figure~\ref{fig:ROC}). For both Voronoi and regions defined as in Section~\ref{subsec:Segmentation}, we consider the two extreme configurations where alerts are raised at the first region firing an outlier or when $K-1$ regions simultaneously fire outliers.

We recorded $8$ sequences from webcams monitoring different urban areas, yielding overall $24410$ frames. From each frame we have cropped the central area, removing the 50 top-most and bottom-most rows, and the 50 left-most and right-most columns\footnote{Sequences can be provided upon request.}. We have synthetically introduced $5\%$ of tampered frames: displacements have been simulated by moving the central cropping area of a random shift having magnitude between 20 and 50 rows and coulumns (as in Figure \ref{fig:sequences}(b)). Blurring  (as in Figure \ref{fig:sequences}(a)) was simulated by convolution against a Gaussian kernel, with $1\leq\sigma\leq5$ randomly defined. 
%\gi{Adriano: image sizes? blur kernel std? quanti pixel il displacement?}
%The second dataset was recorded using a Raspberry Pi Model B+ \cite{raspberry} mounting a camera module. 
%Few sequences of the first dataset contain real tampering events  (Figure \ref{fig:indicatori}). 
%In the second dataset, tampering was introduced by moving the device or spraying water on the camera lens.

A typical figure of merit for assessing detection performance is the Receiver-Operating Characteristic (ROC) curve, where each point corresponds to a pair (FPR$_\gamma$, TPR$_\gamma$) defined as
%
\[\text{FPR}_\gamma = \frac{\text{FP}_\gamma}{\text{TN}_\gamma+\text{FP}_\gamma}, \ \text{ and } \ \text{TPR}_\gamma=\frac{\text{TP}_\gamma}{\text{TP}_\gamma+\text{FN}_\gamma}.\]
%
Here, TP$_\gamma$ represents the number of true positives (tampered frames correctly detected), FP$_\gamma$ of false positives (tampering-free frames detected), TN$_\gamma$ of true negatives (tampering-free frames not detected) and FN$_\gamma$ of false negatives (missed tampered frames), for a given value of $\gamma$. ROC curves have been computed by varying $\gamma_l$, $\gamma_d$ and $\gamma_g$ in a range of values between $0.1$ and $50$. 
\vspace{-0.3cm}
\subsubsection{Discussion}
ROC curves in Figure~\ref{fig:ROC}(a)-(b) and the Area Under the Curve (AUC) values reported in the caption confirm that camera displacements can be better detected by monitoring FD than luma, and that it is convenient to define regions segmenting the scene content. As an example, if we set $\gamma_d = 15.6$, Algorithm~\ref{alg:DISPL} operates at $\text{FPR} = 1\%$ and detects nearly all tampering since $\text{TPR} = 99.92\%$. In contrast, to achieve $\text{FPR} = 1\%$ when monitoring the whole image, FPR drops to $91.67\%$ ($\gamma_d = 6.5$), and when considering Voronoi to $\text{TPR} = 89.05\%$ ($\gamma_d = 18.64$). When monitoring $l$, Algorithm~\ref{alg:DISPL} achieves TPR~=~$73.98\%$ at $\text{FPR}=1\%$  ($\gamma_d=5.8$), while monitoring the whole image is quite ineffective ($\text{TPR} = 17.85\%$, $\gamma_d=3.7$), and similarly perform Voronoi's regions ($\text{FPR} = 53.02\%$, $\gamma_d=6$). We remark that, in the considered low-power scenario, it is important to operate at low FPR, given the large number of frames that smart cameras have to process over time and the cost of data-transmission in terms of battery power. As far as the values of $\Gamma_d$ and $\Gamma_l$ are concerned, the most effective configuration consists in raising an alert as soon as a single region fires a very clear outlier, which implies setting quite wide intervals~\eqref{eq:confidenceRegions}. This option is also preferable because it enables the detection of partial occlusions of the scene.

%\gi{Aggiornare con i nuovi dati}
%\emph{Considering $d$ as indicator, we observe that to achieve a recall of $98\%$, Algorithm~\ref{alg:DISPL} operates at $0.4\%$ of false alarms, with $\gamma = 24.7$, which is less than one fifth of the whole image solution ($2.2\%$ with $\gamma = 4.6$) and the Voronoi solution ($2.3\%$ with $\gamma = 12.9$).
%On the other side, considering $l$ as indicator, we observe that to achieve a recall of $98\%$, Algorithm~\ref{alg:DISPL} operates at $13\%$ of false alarms, with $\gamma = 2.5$, which is about one sixth of the whole image solution ($75\%$ with $\gamma = 0.1$) and about three fifty than the Voronoi solution ($22\%$ with $\gamma = 1.7 $).
%Having few false alarms is important in a low-power context, considering the high number of frames that have to be processed. Most importantly, false alerts are halved basically at no computational overhead.} \gi{Aggiornare con i nuovi dati}
Figure~\ref{fig:ROC}(c) confirms that blurring is more effectively detected by monitoring the whole image at once. This is probably due to the fact that, typically, regions do not include the most prominent edge of the scene, which are indeed the most informative parts to detect blurring. This is the reason why, in Algorithm~\ref{alg:DISPL}, $g$ is monitored on the whole image.%\gi{aggiungere commento su K-1 vornoi che va meglio?}

\begin{figure}[t]
\centering
\includegraphics[width=1\linewidth]{Immagini/curve}
\caption{\textbf{(a)} ROC curves relative to displacement detection based on FD: the AUC obtained by 
``One region - Algorithm 1'' is $99.89\%$, while the AUC obtained by ``Total'' (on the whole 
image) is $99.65\%$.
\textbf{(b)} ROC curves relative to displacement detection based on Luma: the AUC obtained by 
``One region - Algorithm 1'' is $98.44\%$, while the AUC obtained by ``Total'' (on the whole 
image) is $84.07\%$.
\textbf{(c)} ROC curves relative to blurring detection based on Gradient: as opposed to \textbf{(a)} and 
\textbf{(b)}, ``One region - Algorithm 1'' (AUC $98.4\%$) is outperformed by ``Total'' (AUC $99.13\%$).
To highlight differences, the ROC curves in \textbf{(a)} and \textbf{(c)} are drawn in a different TPR, FPR interval.}
%\caption{\textbf{(a)} ROC curve for displacement detection considering Frame Difference (FD) as indicator.
%	%There is an improvement in the performance considering adaptive regions w.r.t. considering the whole image or Voronoi regions.
%	The AUC corresponding to Algorithm~\ref{alg:DISPL} ($1$ region - Algorithm $1$) is $99.89\%$, while the AUC of considering the whole image (Total) is $99.65\%$. 
%	%the AUC of Luma-Voronoi is $99.85\%$, and the AUC of Frame-Difference is $99.44\%$ (axis have been zoomed for the visualization sake). Large AUC values indicate that these displacements can be successfully detected and that Algorithm~\ref{alg:DISPL} is the most effective one.
%	\textbf{(b)} ROC curve for displacement detection considering Luma as indicator.
%	%There is an improvement in the performance considering adaptive regions w.r.t. considering the whole image or Voronoi regions.
%	The AUC corresponding to Algorithm~\ref{alg:DISPL} ($1$ region - Algorithm $1$) is $98.44\%$, while the AUC of considering the whole image (Total) is $84.07\%$. 
%	\textbf{(c)} ROC curve for blurring detection.
%	In this case, the Gradient-Total (AUC $99.13\%$) outperforms the Gradient-Regions (AUC $98.4\%$) because this latter do not include the most prominent edges in images, which are the most important information to detect blurring. %This is the reason why, in Algorithm~\ref{alg:DISPL}, $g$ is monitored on the whole image. 
%	ROC curves \textbf{(a)} and \textbf{(c)}
%	%For the visualization sake, ROC curves \textbf{(a)} and \textbf{(c)} have been reported in a limited range of both axis, and in particular we focus on low values of 1-SPECIFICITY, thus of false alarms.
	%}
\label{fig:ROC}
\end{figure}
%\begin{figure}[htb]
%\centering
%\subfigure[]{\label{fig:buenosAiresDef}\includegraphics[width=0.45\linewidth]{Immagini/ROCdefocus1}}
%\subfigure[]{\label{fig:buenosAiresDispl} \includegraphics[width=0.45\linewidth]{Immagini/ROCdefocus_fd}}
%\caption{ROC curves for defocus detection, considering three alternative approaches. \textbf{(a)} Analysis of the mean gradient energy. \textbf{(b)} Analysis of the frame differencing.}
%\label{fig:ROCdisplacement}
%\label{fig:ROCdefocus}
%\end{figure}
